---
title: "E.Sun Data"
author: "Helen Chang"
output:
  ioslides_presentation:
    transition: faster
---


## Datasets  
- ETAB  
- Call Center Inbound  


# ETAB  


## ETAB  
- Currently is counted by ticket number (not exactly the amount of people)  
```{r echo=FALSE, results='hide', cache=TRUE}
library(data.table)
library(stringr)
library(plyr)
is.windows <- function() .Platform$OS.type=="windows"
ifelse(is.windows(), setwd("D:/E-sun"), setwd('/home/esunb/Helen/'))
f.name <- "cleaned_ETAB.csv"
# read in etab
etab <- read.csv(f.name, fileEncoding = "UTF-8", 
                 colClasses = c("character", "character", "character", "character",
                                "character", "character", "character", "integer",
                                "integer", "integer", "integer", "character", 
                                "character", "character", "character"))
etab$in.dtm <- strptime(etab$in.dtm, format = "%Y-%m-%d %H:%M:%S")

brh.geo <- read.csv("brh.addr.csv", fileEncoding = "UTF-8",
                   colClasses = c("character", "character", "character", "character", 
                                  "character"))
for(x in 2:6) {
    brh.geo[[x]] <- str_trim(brh.geo[[x]])
}
colnames(brh.geo) <- c("brh", "brh.name", "brh.zip", "brh.addr", "brh.lat", "brh.lng")

# added call center inbound
f.name <- "cleaned_call.csv"
call <- fread(f.name, data.table=F)
setnames(call, c("act.id", "seq.no", "cu.id", "cu.id.md5", "call.dt", "opr.id", 
                 "opr.id.md5", "rsn.id1", "rsn.1", "rsn.id2", "rsn.2", 
                 "rsn.id3", "rsn.3", "call.type", "type.descr"))
call$call.dt <- strptime(call$call.dt, format="%Y-%m-%d")


# function
p.serv.sec <- function(brh.code="0679", date="2014-10-01"){
    y <- etab[etab$brh==brh.code&etab$in.dt==date, c("tkt.no", "serv.sec")]    
    y$tkt.no <- as.integer(y$tkt.no)
    y <- y[order(y$tkt.no),]
    y <- y[y$tkt.no<700,]
    main <- paste("brh", brh.code, date, sep=" ")
    
#     pdf(file = paste0(i, main, ".pdf"), width = 10, height=5)
    with(y, plot(serv.sec~tkt.no, pch=1, cex=.6, main=main))
#     dev.off()
}
```
- `r dim(etab)[1]` tkts in total  
- `r length(unique(etab$clerk.card))` clerks among `r length(unique(etab$brh)) ` branches  
- The columns in ETAB (cleaned):  
```{r echo=FALSE, cache=TRUE}
colnames(etab)
```  
- "VIPNO" & "ikey" ignored  


## Total Tickets by Date  
- Hoildays instered  
- Anomaly CW11 (2015-03-09)  
```{r echo=FALSE, cache=TRUE}
t.in.dt <- data.frame(table(etab$in.dt))
colnames(t.in.dt)[1] <- "in.dt"
t.in.dt$in.dt <- as.Date(as.character(t.in.dt$in.dt))
seq <- seq(as.Date("2014-10-01"), as.Date("2015-03-31"), by = "day")
tmp <- data.frame(in.dt = seq[!(seq %in% t.in.dt$in.dt)], Freq = NA)
t.in.dt <- rbind(t.in.dt, tmp)
t.in.dt <- t.in.dt[order(t.in.dt$in.dt),]

par(mar = c(8,4,2,2))
plot(t.in.dt$Freq, type = "h", ylab = "Amount of tickets", xlab = "", xaxt = "n")
xaxt.tick <- seq(6, by = 7, length.out = 26)
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
```  


## Calls by Date  
- Anomaly CW11 (2015-03-09)  
```{r echo=FALSE, cache=TRUE}
t.call.dt <- count(call, vars="call.dt")
t.call.dt$call.dt <- as.Date(as.character(t.call.dt$call.dt))
tmp2 <- data.frame(call.dt = seq[!(seq %in% t.call.dt$call.dt)], freq = NA)

t.call.dt <- rbind(t.call.dt, tmp2)
t.call.dt <- t.call.dt[order(t.call.dt$call.dt),]

par(mar = c(8,4,2,2))
plot(t.call.dt$freq, type = "h", ylab = "Amount of calls", xlab = "", xaxt = "n")
xaxt.tick <- seq(6, by = 7, length.out = 26)
axis(1, at = xaxt.tick, labels = as.character(t.call.dt$call.dt)[xaxt.tick], las = 2)
```  


## Customer Types  
- Tkts of each customer groups:  
```{r echo=FALSE, cache=TRUE}
table(etab$cu.grp)
```  
- Tkts of each catogories:  
```{r echo=FALSE, cache=TRUE}
table(etab$sale.no)
```  
>- A = 一般收付 + VVIP + VIP;  
     1~700 (GRP1) + 901~950 (GRP4) + 951~999 (GRP5)  
>- B = 外匯服務：701~800 (GRP2);  
>- C = 服務中心：801~900 (GRP3)  


## Total Tickets by Date  
- GRP1~5 included  
```{r echo=FALSE, cache=TRUE}
t.in.dt <- data.frame(table(etab$in.dt))
t1.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP1"]))
t2.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP2"]))
t3.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP3"]))
t4.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP4"]))
t5.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP5"]))
colnames(t.in.dt)[1] <- "in.dt"
colnames(t1.in.dt)[1] <- "in.dt"
colnames(t2.in.dt)[1] <- "in.dt"
colnames(t3.in.dt)[1] <- "in.dt"
colnames(t4.in.dt)[1] <- "in.dt"
colnames(t5.in.dt)[1] <- "in.dt"
t.in.dt$in.dt <- as.Date(as.character(t.in.dt$in.dt))
t1.in.dt$in.dt <- as.Date(as.character(t1.in.dt$in.dt))
t2.in.dt$in.dt <- as.Date(as.character(t2.in.dt$in.dt))
t3.in.dt$in.dt <- as.Date(as.character(t3.in.dt$in.dt))
t4.in.dt$in.dt <- as.Date(as.character(t4.in.dt$in.dt))
t5.in.dt$in.dt <- as.Date(as.character(t5.in.dt$in.dt))

seq <- seq(as.Date("2014-10-01"), as.Date("2015-03-31"), by = "day")
tmp <- data.frame(in.dt = seq[!(seq %in% t.in.dt$in.dt)], Freq = NA)

t.in.dt <- rbind(t.in.dt, tmp)
t.in.dt <- t.in.dt[order(t.in.dt$in.dt),]
t1.in.dt <- rbind(t1.in.dt, tmp)
t1.in.dt <- t1.in.dt[order(t1.in.dt$in.dt),]
t2.in.dt <- rbind(t2.in.dt, tmp)
t2.in.dt <- t2.in.dt[order(t2.in.dt$in.dt),]
t3.in.dt <- rbind(t3.in.dt, tmp)
t3.in.dt <- t3.in.dt[order(t3.in.dt$in.dt),]
t4.in.dt <- rbind(t4.in.dt, tmp)
t4.in.dt <- t4.in.dt[order(t4.in.dt$in.dt),]
t5.in.dt <- rbind(t5.in.dt, tmp)
t5.in.dt <- t5.in.dt[order(t5.in.dt$in.dt),]

xaxt.tick <- seq(6, by = 7, length.out = 26)
type = "l"

library(RColorBrewer)
clr <- brewer.pal(8, "Set1")[c(1,2,8,4,5,3)]
lbl <- c("All", "G1", "FX", "Serv", "VVIP", "VIP")

par(mar = c(6,4,2,2))
plot(t.in.dt$Freq, type = type, ylab = "Amount of tickets", xlab = "", xaxt = "n", 
     ylim = c(0, 65000), col=clr[1])
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
lines(t1.in.dt$Freq, col=clr[2])
lines(t2.in.dt$Freq, col=clr[3])
lines(t3.in.dt$Freq, col=clr[4])
lines(t4.in.dt$Freq, col=clr[5])
lines(t5.in.dt$Freq, col=clr[6])
legend(y=68000, x=-5, legend = lbl, col = clr, ncol = 2, cex = .8, lwd = 3, 
       text.col = clr, bty="n")
```  


## Total Tickets by Date (GRP2~5)  
- Zoom into GRP2~5  
```{r echo=FALSE, cache=TRUE}
par(mar = c(6,4,2,2))
plot(t2.in.dt$Freq, type = type, ylab = "Amount of tickets", xlab = "", xaxt = "n", 
     ylim = c(0, 5500), col=clr[3])
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
lines(t3.in.dt$Freq, col=clr[4])
lines(t4.in.dt$Freq, col=clr[5])
lines(t5.in.dt$Freq, col=clr[6])
legend(y=5500, x=-5, legend = lbl[3:6], col = clr[3:6], ncol = 2, cex = .8, 
       lwd = 3, text.col = clr[3:6], bty="n")
```  


## Ticket No. in Total  
- The "skipped ticket" is still included  
```{r echo=FALSE, cache=TRUE}
plot(table(etab$tkt.no), ylab="Amount of tikets", xlab="Ticket no.")
```  


## Ticket No.  
- Once reaching the upper limit of ticket no., the counter will return to _01  
- None of "0950" & "1000"  
```{r echo=FALSE, cache=TRUE}
etab[etab$tkt.no=="0700"|etab$tkt.no=="0800"|etab$tkt.no=="0900"|etab$tkt.no=="0950"|etab$tkt.no=="1000", c("brh", "tkt.no", "in.dtm")]
```  


## Service Time: Minus Values  
- Reason remains unknown  
```{r echo=FALSE, cache=TRUE}
etab[etab$serv.sec<0, c("brh", "tkt.no", "serv.sec", "in.dtm", "sta.tm")]
```  


## Mean Service Time (by Branch)  
```{r echo=FALSE, cache=TRUE}
avg.brh.serv <- aggregate(serv.sec~brh, data = etab, FUN="mean")
colnames(avg.brh.serv)[2] <- "avg.serv.sec"
avg.brh.serv <- join(brh.geo[,c("brh", "brh.name")], avg.brh.serv, by = "brh")
avg.brh.serv <- avg.brh.serv[order(avg.brh.serv$avg.serv.sec),]
data.table(avg.brh.serv)
```  


## Mean Service Time (by Branch)  
- Split roughly from 15 sec (will be examined later)  
- Then sort by lt15.pct  
```{r echo=FALSE, cache=TRUE}
serv.lt15 <- etab[etab$serv.sec<=15, ]
serv.mt15 <- etab[etab$serv.sec>15, ]

brh.serv.sec <- data.frame(aggregate(serv.sec~brh, data = serv.lt15, count))

brh.lt15 <- count(serv.lt15, vars = "brh")
brh.mt15 <- count(serv.mt15, vars = "brh")
brh.total <- count(etab, vars = "brh")
brh.serv.sec <- data.table(brh = brh.total$brh,
                           serv.total = brh.total$freq,
                           lt15.pct = brh.lt15$freq*100/brh.total$freq)

avg.brh.serv <- aggregate(serv.sec~brh, data = etab, FUN="mean")
colnames(avg.brh.serv)[2] <- "avg.serv.sec"
avg.brh.serv <- join(brh.geo[,c("brh", "brh.name")], avg.brh.serv, by = "brh")

brh.serv.sec <- join(brh.serv.sec, avg.brh.serv, by = "brh")
brh.serv.sec <- brh.serv.sec[order(brh.serv.sec$lt15.pct, decreasing=T),]
brh.serv.sec
```  


## Mean Service Time (001~700)  
- Rank 1 `r brh.geo$brh.name[brh.geo$brh==brh.serv.sec$brh[1]]`
```{r echo=FALSE, cache=TRUE}
p.serv.sec(brh.code=brh.serv.sec$brh[1], date = "2014-12-15")
```  


## Mean Service Time (001~700)  
- Rank 130 `r brh.geo$brh.name[brh.geo$brh==brh.serv.sec$brh[130]]`
```{r echo=FALSE, cache=TRUE}
p.serv.sec(brh.code=brh.serv.sec$brh[130], date = "2014-12-15")
```  


## Least-20 of Service Time  
```{r echo=FALSE, cache=TRUE}
cbind(brh.serv.sec[1:10, .(brh, brh.name)], rank=11:20, brh.serv.sec[11:20, .(brh, brh.name)])
```  


## Service Time Filtering  
- First exclude the branches with service time least-20  
- Then filter out service time which is less-than-15secs  
```{r echo=FALSE, cache=TRUE, results='hide'}
# etab.l <- etab[(!etab$brh %in% brh.serv.sec$brh[1:20])&(etab$serv.sec<=15),]
etab.f <- etab[(!etab$brh %in% brh.serv.sec$brh[1:20])&(etab$serv.sec>15),]
summary(etab.f$serv.sec)
```  


## Service Time Filtered (GRP1~5)  
```{r echo=FALSE, cache=TRUE}
grp.brh.serv <- aggregate(serv.sec~brh+cu.grp, data = etab.f, FUN="mean")
colnames(grp.brh.serv)[3] <- "avg.serv.sec"
boxplot(grp.brh.serv$avg.serv.sec ~ grp.brh.serv$cu.grp, 
        ylab = "Mean service seconds", xaxt = "n")
axis(1, at = 1:5, labels = c("Normal", "FX", "S.center", "VVIP", "VIP"))
```  


## Waiting Time Filtered (GRP1~5)  
```{r echo=FALSE, cache=TRUE}
grp.brh.wait <- aggregate(wait.sec~brh+cu.grp, data = etab.f, FUN="mean")
colnames(grp.brh.wait)[3] <- "avg.wait.sec"
boxplot(grp.brh.wait$avg.wait.sec ~ grp.brh.wait$cu.grp, 
        ylab = "Mean waiting seconds", xaxt = "n")
axis(1, at = 1:5, labels = c("Normal", "FX", "S.center", "VVIP", "VIP"))
```  


## Info by Branches (.csv)  
```{r echo=FALSE, cache=TRUE}
ss <- fread("brh.info.csv")
head(ss)
```



# Call Center Inbound  



## Operators (.csv)  
```{r echo=FALSE, cache=TRUE}
opr <- fread("opr.info.csv")
head(opr)
```  


# Thank you  