---
title: "E.Sun Data First Peek"
author: "Helen Chang"
output:
  ioslides_presentation:
    transition: faster
---


## Datasets  
- ETAB  
- Call Center Inbound  


## Data Cleaning  
- Change encoding from cp950 to UTF-8  
- Trim white-space  
- Rename columns  


# ETAB


## ETAB  
- Currently is counted by ticket number (not exactly the amount of people)
```{r echo=FALSE, results='hide', cache=TRUE}
library(data.table)
library(stringr)
library(plyr)
is.windows <- function() .Platform$OS.type=="windows"
ifelse(is.windows(), setwd("D:/E-sun"), setwd('/home/esunb/Helen/'))
# ifelse(is.windows(), f.name <- "ETABS0.D", f.name <- "cleaned_ETAB.csv")
f.name <- "cleaned_ETAB.csv"
# getwd()

# write.csv(etab, "cleaned_ETAB.csv", fileEncoding="UTF-8", row.names=F)
etab <- read.csv(f.name, fileEncoding = "UTF-8", 
                 colClasses = c("character", "character", "character", "character",
                                "character", "character", "character", "integer",
                                "integer", "integer", "integer", "character", 
                                "character", "character", "character"))
etab$in.dtm <- strptime(etab$in.dtm, format = "%Y-%m-%d %H:%M:%S")

brh.geo <- read.csv("brh.geo.u.csv", fileEncoding = "UTF-8",
                   colClasses = c("character", "character", "character", "character", 
                                  "character"))
for(x in 2:6) {
    brh.geo[[x]] <- str_trim(brh.geo[[x]])
}
colnames(brh.geo) <- c("brh", "brh.name", "brh.zip", "brh.addr", "brh.lat", "brh.lng")
```
- `r dim(etab)[1]` tkts in total
- `r length(unique(etab$clerk.card))` clerks among `r length(unique(etab$brh)) ` branches  
- The columns in ETAB (cleaned):  
```{r echo=FALSE, cache=TRUE}
colnames(etab)
```  
- Ignore /VIPNO/ & /ikey/


## Total Tickets by Date  
- hoildays instered
```{r echo=FALSE, cache=TRUE}
t.in.dt <- data.frame(table(etab$in.dt))
colnames(t.in.dt)[1] <- "in.dt"
t.in.dt$in.dt <- as.Date(as.character(t.in.dt$in.dt))
seq <- seq(as.Date("2014-10-01"), as.Date("2015-03-31"), by = "day")
tmp <- data.frame(in.dt = seq[!(seq %in% t.in.dt$in.dt)], Freq = NA)
t.in.dt <- rbind(t.in.dt, tmp)
t.in.dt <- t.in.dt[order(t.in.dt$in.dt),]

par(mar = c(8,4,2,2))
plot(t.in.dt$Freq, type = "h", ylab = "Amount of tickets", xlab = "", xaxt = "n")
xaxt.tick <- seq(6, by = 7, length.out = 26)
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
```  


## Total Tickets by Date  
- Hoildays instered, and GRP1~5 included  
```{r echo=FALSE, cache=TRUE}
t.in.dt <- data.frame(table(etab$in.dt))
t1.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP1"]))
t2.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP2"]))
t3.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP3"]))
t4.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP4"]))
t5.in.dt <- data.frame(table(etab$in.dt[etab$cu.grp=="GRP5"]))
colnames(t.in.dt)[1] <- "in.dt"
colnames(t1.in.dt)[1] <- "in.dt"
colnames(t2.in.dt)[1] <- "in.dt"
colnames(t3.in.dt)[1] <- "in.dt"
colnames(t4.in.dt)[1] <- "in.dt"
colnames(t5.in.dt)[1] <- "in.dt"
t.in.dt$in.dt <- as.Date(as.character(t.in.dt$in.dt))
t1.in.dt$in.dt <- as.Date(as.character(t1.in.dt$in.dt))
t2.in.dt$in.dt <- as.Date(as.character(t2.in.dt$in.dt))
t3.in.dt$in.dt <- as.Date(as.character(t3.in.dt$in.dt))
t4.in.dt$in.dt <- as.Date(as.character(t4.in.dt$in.dt))
t5.in.dt$in.dt <- as.Date(as.character(t5.in.dt$in.dt))

seq <- seq(as.Date("2014-10-01"), as.Date("2015-03-31"), by = "day")
tmp <- data.frame(in.dt = seq[!(seq %in% t.in.dt$in.dt)], Freq = NA)

t.in.dt <- rbind(t.in.dt, tmp)
t.in.dt <- t.in.dt[order(t.in.dt$in.dt),]
t1.in.dt <- rbind(t1.in.dt, tmp)
t1.in.dt <- t1.in.dt[order(t1.in.dt$in.dt),]
t2.in.dt <- rbind(t2.in.dt, tmp)
t2.in.dt <- t2.in.dt[order(t2.in.dt$in.dt),]
t3.in.dt <- rbind(t3.in.dt, tmp)
t3.in.dt <- t3.in.dt[order(t3.in.dt$in.dt),]
t4.in.dt <- rbind(t4.in.dt, tmp)
t4.in.dt <- t4.in.dt[order(t4.in.dt$in.dt),]
t5.in.dt <- rbind(t5.in.dt, tmp)
t5.in.dt <- t5.in.dt[order(t5.in.dt$in.dt),]

xaxt.tick <- seq(6, by = 7, length.out = 26)
type = "l"

library(RColorBrewer)
clr <- brewer.pal(8, "Set1")[c(1,2,8,4,5,3)]
lbl <- c("All", "G1", "FX", "Serv", "VVIP", "VIP")

par(mar = c(8,4,2,2))
plot(t.in.dt$Freq, type = type, ylab = "Amount of tickets", xlab = "", xaxt = "n", 
     ylim = c(0, 65000), col=clr[1])
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
lines(t1.in.dt$Freq, col=clr[2])
lines(t2.in.dt$Freq, col=clr[3])
lines(t3.in.dt$Freq, col=clr[4])
lines(t4.in.dt$Freq, col=clr[5])
lines(t5.in.dt$Freq, col=clr[6])
legend(y=20000, x=5, legend = lbl, col = clr, ncol = 1, cex = .8, lwd = 3, text.col = clr)
```  


## Total Tickets by Date (GRP2~5)  
- Hoildays instered, zoom into GRP2~5  
```{r echo=FALSE, cache=TRUE}
par(mar = c(8,4,2,2))
plot(t2.in.dt$Freq, type = type, ylab = "Amount of tickets", xlab = "", xaxt = "n", 
     ylim = c(0, 5500), col=clr[3])
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
lines(t3.in.dt$Freq, col=clr[4])
lines(t4.in.dt$Freq, col=clr[5])
lines(t5.in.dt$Freq, col=clr[6])
legend(y=5500, x=5, legend = lbl[3:6], col = clr[3:6], ncol = 1, cex = .8, lwd = 3, text.col = clr[3:6])
```  


## Mean Tickets by Date  
- hoildays instered
```{r echo=FALSE, cache=TRUE}
c.brh <- count(etab, vars=c("brh", "in.dt"))
c.brh$mday <- strptime(c.brh$in.dt, "%Y-%m-%d")$mday
par(mar = c(8,4,2,2))
boxplot(c.brh$freq ~ c.brh$wday, ylab = "Average amount of tickets", xaxt = "n")
plot(t.in.dt$Freq, type = "h", ylab = "Amount of tickets", xlab = "", xaxt = "n")
xaxt.tick <- seq(6, by = 7, length.out = 26)
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
```  


## Mean Tickets by Weekdays
```{r echo=FALSE, cache=TRUE}
# c.brh.cu <- count(etab, vars=c("brh", "in.dt", "cu.grp"))
c.brh.cu$wday <- strptime(c.brh.cu$in.dt, "%Y-%m-%d")$wday
boxplot(c.brh.cu$freq ~ c.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")
axis(1, at = 1:5, labels = c("Mon", "Tue", "Wed", "Thr", "Fri"))

c1.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP1",]
boxplot(c1.brh.cu$freq ~ c1.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c2.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP2",]
boxplot(c2.brh.cu$freq ~ c2.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c3.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP3",]
boxplot(c3.brh.cu$freq ~ c3.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c4.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP4",]
boxplot(c4.brh.cu$freq ~ c4.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c5.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP5",]
boxplot(c5.brh.cu$freq ~ c5.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

```  


## Total Tickets Every Half-hour  
- Time blocks (0-48) were transformed to (0-24)  
```{r echo=FALSE, cache=TRUE}
# sta <- strptime("2015-03-30", format = "%Y-%m-%d")
# end <- strptime("2015-03-31", format = "%Y-%m-%d")
# s <- strftime(seq(sta, end, by = "1 hour"), format = "%H:%M")[-25]

t.tm.blk <- table(etab$tm.blk)
dimnames(t.tm.blk) <- list((1:48)/2)
barplot(t.tm.blk, xlab = "Every 30-mins",
        ylab = "Total tickets", space = 1)
```  


## Total Tickets Every Half-hour  
- It seemed the time stamps were contaminated  
- Need further examination
```{r echo=FALSE, cache=TRUE}
t.tm.blk
```  


## Daily Tickets of Branches (Rank)  
```{r echo=FALSE, cache=TRUE}
avg.tkt.brh <- aggregate(freq~brh, data=c.brh, mean)
colnames(avg.tkt.brh)[2] <- "mean"
avg.tkt.brh$sd <- aggregate(freq~brh, data=c.brh, sd)[, 2]
avg.tkt.brh <- avg.tkt.brh[order(avg.tkt.brh$mean, decreasing=T), ]
avg.tkt.brh <- join(brh.geo[, c(1, 2)], avg.tkt.brh, by="brh", type="right")
colnames(avg.tkt.brh)[3:4] <- c("avg.tkt", "sd.tkt")
avg.tkt.brh <- data.table(avg.tkt.brh)
avg.tkt.brh
```  

Summary:
```{r echo=FALSE, cache=TRUE}
summary(avg.tkt.brh$avg.tkt)
```  


## Ticket No. in Total  
- The "skipped ticket" is still included
```{r echo=FALSE, cache=TRUE}
plot(table(etab$tkt.no), ylab="Amount of tikets", xlab="Ticket no.")
```  



## Customer Types  
- Tkts of each customer groups:  
```{r echo=FALSE, cache=TRUE}
table(etab$cu.grp)
```  
- Tkts of each catogories:  
```{r echo=FALSE, cache=TRUE}
table(etab$sale.no)
```  
>- A = 一般收付 + VVIP + VIP;  
     1~700 (GRP1) + 901~950 (GRP4) + 951~999 (GRP5)
>- B = 外匯服務：701~800 (GRP2);  
>- C = 服務中心：801~900 (GRP3)


## Waiting and Service Time  
```{r}
summary(etab$wait.sec)
summary(etab$serv.sec)
```  


## Service Time  
```{r echo=FALSE, cache=TRUE}
serv.sec <- table(etab$serv.sec)
plot(serv.sec, xlab="Service time (sec)", ylab ="Amount of tickets")
```  


## Service Time  
```{r echo=FALSE, cache=TRUE}
serv.sec.0to1hr <- table(etab$serv.sec[etab$serv.sec>0&etab$serv.sec<=3600])
plot(serv.sec.0to1hr[10:730], xaxt = "n", xlab="Service time (sec)", ylab ="Amount of tickets")
axis(1, at=0:720, labels=10:730)
```  


## Waiting Time  
```{r echo=FALSE, cache=TRUE}
wait.sec <- table(etab$wait.sec)
plot(wait.sec, xlab="Service time (sec)", ylab ="Amount of tickets")
```  


## Waiting Time  
```{r echo=FALSE, cache=TRUE}
wait.tm.0to1hr <- table(etab$wait.sec[etab$wait.sec>=0&etab$wait.sec<3600])
plot(wait.tm.0to1hr[1:720], xaxt = "n", xlab="Waiting time (sec)", ylab ="Amount of tickets")
axis(1, at=1:720, labels=1:720)
```  


## Later-on Analysis  
- check the contanminated time span  
- filter out the skipped tkts  
- customer/datetime/branch/clerk  
- ...and so on  



# Call Center Inbound  


## Call Center Inbound  
```{r echo=FALSE, results='hide', cache=TRUE}
f.name <- "cleaned_call.csv"
call <- fread(f.name, data.table=F)
setnames(call, c("act.id", "seq.no", "cu.id", "cu.id.md5", "call.dt", "opr.id", 
                 "opr.id.md5", "rsn.id1", "rsn.1", "rsn.id2", "rsn.2", 
                 "rsn.id3", "rsn.3", "call.type", "type.descr"))
call$call.dt <- strptime(call$call.dt, format="%Y-%m-%d")
```  
- `r length(unique(call$cu.id.md5))` customers called  
- With `r length(unique(call$opr.id.md5))` operators  
- The columns in call-center-inbound (cleaned):  
```{r echo=FALSE, cache=TRUE}
colnames(call)
```


## Calls by Date  
```{r echo=FALSE, cache=TRUE}
t.call.dt <- count(call, vars="call.dt")
par(mar = c(8,4,2,2))
barplot(t.call.dt$freq, ylab = "Amount of calls", names.arg = t.call.dt$call.dt)
```  


## Average Calls by Weekdays  
```{r echo=FALSE, cache=TRUE}
t.call.dt$wday <- t.call.dt$call.dt$wday
# a.call.wday <- aggregate(freq~wday, data= t.call.dt, mean)
boxplot(t.call.dt$freq ~ t.call.dt$wday, ylab = "Average amount of calls", xaxt = "n")
axis(1, at = 1:7, labels = c("Sun", "Mon", "Tue", "Wed", "Thr", "Fri", "Sat"))
```  


## Call-in Reasons (Rank)  
- In `r length(unique(call$rsn.id1))` catogories:
```{r echo=FALSE, cache=TRUE}
t.call.rsn <- table(call$rsn.id1)
t.call.rsn
```  



## Call-in Reasons (Rank)  
- M: 信用卡帳務問題  
- N: 信用卡製卡/掛失/授權/使用詢問  
- AD: 卡片附加優惠(保險/停車/貴賓室/道救)  
```{r echo=FALSE, cache=TRUE}
plot(t.call.rsn)
```  


## Call-in Reasons (Rank)  
- M: 信用卡帳務問題 **(帳單查詢、繳款查詢)**  
- N: 信用卡製卡/掛失/授權/使用詢問 **(額度查詢)**  
- AD: 卡片附加優惠(保險/停車/貴賓室/道救)  
```{r echo=FALSE, cache=TRUE}
plot(table(call$rsn.id2))
```  
 


## Call type  
```{r cache=TRUE}
table(call$call.type)
```  


## Later-on Analysis  
- bind with customer type analysis  
- cost analysis  
- ...and so on  


# Thank you