
## Mean Waiting Time of Each Group
```{r echo=FALSE, cache=TRUE}
m.wtm.grp <- aggregate(wait.sec ~ in.dt + cu.grp, data=etab, mean)
par(mar = c(8,4,2,2))
boxplot(m.wtm.grp$wait.sec ~ m.wtm.grp$cu.grp, ylab = "Average amount of tickets", xaxt = "n")
```



## Abnormal Branch Behavior (15secs)  
```{r echo=FALSE, cache=TRUE}
serv.lt15 <- etab[etab$serv.sec<=15, ]
serv.mt15 <- etab[etab$serv.sec>15, ]

brh.serv.sec <- data.frame(aggregate(serv.sec~brh, data = serv.lt15, count))

brh.serv.sec <- data.table(brh = count(serv.lt15, vars = "brh")$brh,
                           serv.lt15 = count(serv.lt15, vars = "brh")$freq,
                           serv.mt15 = count(serv.mt15, vars = "brh")$freq,
                           serv.total = count(etab, vars = "brh")$freq)
brh.serv.sec[,lt15.pct:=round(serv.lt15*100/serv.total, 1)]
brh.serv.sec[,mt15.pct:=round(serv.mt15*100/serv.total, 1)]
brh.serv.sec <- brh.serv.sec[order(brh.serv.sec$lt15.pct, decreasing=T),]

x <- aggregate(serv.sec~brh, data = etab, FUN="mean")
x <- x[order(x$serv.sec),]

brh.serv.sec <- join(brh.serv.sec, x, by = "brh")



brh.serv.sec <- data.frame(in.dt = count(serv.lt15, vars = c("in.dt", "cu.grp"))$in.dt,
                           cu.grp = count(serv.lt15, vars = c("in.dt", "cu.grp"))$cu.grp,                           
                           serv.lt15 = count(serv.lt15, vars = c("in.dt", "cu.grp"))$freq,
                           serv.mt15 = count(serv.mt15, vars = c("in.dt", "cu.grp"))$freq,
                           serv.total = count(etab, vars = c("in.dt", "cu.grp"))$freq)


```  


## Abnormal Branch Behavior (5sec)  
```{r echo=FALSE, cache=TRUE}
serv.lt05 <- etab[etab$serv.sec<=5, ]
serv.mt05 <- etab[etab$serv.sec>5, ]

brh.serv.sec <- data.frame(aggregate(serv.sec~brh, data = serv.lt05, count))

brh.serv.sec <- data.table(brh = count(serv.lt05, vars = "brh")$brh,
                           serv.lt05 = count(serv.lt05, vars = "brh")$freq,
                           serv.mt05 = count(serv.mt05, vars = "brh")$freq,
                           serv.total = count(etab, vars = "brh")$freq)
brh.serv.sec[,lt05.pct:=round(serv.lt05*100/serv.total, 1)]
brh.serv.sec[,mt05.pct:=round(serv.mt05*100/serv.total, 1)]
brh.serv.sec <- brh.serv.sec[order(brh.serv.sec$lt05.pct, decreasing=T),]

x <- aggregate(serv.sec~brh, data = etab, FUN="mean")
x <- x[order(x$serv.sec),]

brh.serv.sec <- join(brh.serv.sec, x, by = "brh")
```  


## Older test  


## Mean Tickets by Date  
- hoildays instered
```{r echo=FALSE, cache=TRUE}
c.brh <- count(etab, vars=c("brh", "in.dt"))
c.brh$mday <- strptime(c.brh$in.dt, "%Y-%m-%d")$mday
par(mar = c(8,4,2,2))
boxplot(c.brh$freq ~ c.brh$mday, ylab = "Average amount of tickets", xaxt = "n")
xaxt.tick <- seq(6, by = 7, length.out = 26)
axis(1, at = xaxt.tick, labels = as.character(t.in.dt$in.dt)[xaxt.tick], las = 2)
```  


## Mean Tickets by Weekdays
```{r echo=FALSE, cache=TRUE}
# c.brh.cu <- count(etab, vars=c("brh", "in.dt", "cu.grp"))
c.brh.cu$wday <- strptime(c.brh.cu$in.dt, "%Y-%m-%d")$wday
boxplot(c.brh.cu$freq ~ c.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")
axis(1, at = 1:5, labels = c("Mon", "Tue", "Wed", "Thr", "Fri"))

c1.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP1",]
boxplot(c1.brh.cu$freq ~ c1.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c2.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP2",]
boxplot(c2.brh.cu$freq ~ c2.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c3.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP3",]
boxplot(c3.brh.cu$freq ~ c3.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c4.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP4",]
boxplot(c4.brh.cu$freq ~ c4.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")

c5.brh.cu <- c.brh.cu[c.brh.cu$cu.grp=="GRP5",]
boxplot(c5.brh.cu$freq ~ c5.brh.cu$wday, ylab = "Average amount of tickets", xaxt = "n")
```  


## Total Tickets Every Half-hour  
- Time blocks (0-48) were transformed to (0-24)  
```{r echo=FALSE, cache=TRUE}
# sta <- strptime("2015-03-30", format = "%Y-%m-%d")
# end <- strptime("2015-03-31", format = "%Y-%m-%d")
# s <- strftime(seq(sta, end, by = "1 hour"), format = "%H:%M")[-25]

t.tm.blk <- table(etab$tm.blk)
dimnames(t.tm.blk) <- list((1:48)/2)
barplot(t.tm.blk, xlab = "Every 30-mins",
        ylab = "Total tickets", space = 1)
```  


## Total Tickets Every Half-hour  
- It seemed the time stamps were contaminated  
- Need further examination
```{r echo=FALSE, cache=TRUE}
t.tm.blk
```  


## Daily Tickets of Branches (Rank)  
```{r echo=FALSE, cache=TRUE}
avg.tkt.brh <- aggregate(freq~brh, data=c.brh, mean)
colnames(avg.tkt.brh)[2] <- "mean"
avg.tkt.brh$sd <- aggregate(freq~brh, data=c.brh, sd)[, 2]
avg.tkt.brh <- avg.tkt.brh[order(avg.tkt.brh$mean, decreasing=T), ]
avg.tkt.brh <- join(brh.geo[, c(1, 2)], avg.tkt.brh, by="brh", type="right")
colnames(avg.tkt.brh)[3:4] <- c("avg.tkt", "sd.tkt")
avg.tkt.brh <- data.table(avg.tkt.brh)
avg.tkt.brh
```  
- Summary:
```{r echo=FALSE, cache=TRUE}
summary(avg.tkt.brh$avg.tkt)
```  


## Waiting and Service Time  
```{r}
summary(etab$wait.sec)
summary(etab$serv.sec)
```  


## Service Time  
```{r echo=FALSE, cache=TRUE}
serv.sec <- table(etab$serv.sec)
plot(serv.sec, xlab="Service time (sec)", ylab ="Amount of tickets")
```  


## Service Time  
```{r echo=FALSE, cache=TRUE}
serv.sec.0to1hr <- table(etab$serv.sec[etab$serv.sec>0&etab$serv.sec<=3600])
plot(serv.sec.0to1hr[10:730], xaxt = "n", xlab="Service time (sec)", ylab ="Amount of tickets")
axis(1, at=0:720, labels=10:730)
```  